---
title: "2002_FakeNews_Pilot"
output: html_document
---

Clear Environment and load packages

```{r}
# Clear Environment
rm(list = ls())

# Load packages
library(conflicted)
library(tidyverse)
library(Hmisc)
library(lme4)
library(car)
library(emmeans)
library(gridExtra)
library(tidyr)
library(readxl)
library(zoo)
library(dplyr)
library(reshape2)
library(data.table)
library(magrittr)
library(stringr)
library(GLMMadaptive)
library(pander)

conflict_prefer("filter", "dplyr")
```

Imported data

```{r}
# read data
pilot_data <- read.csv("901-1.csv", stringsAsFactors = FALSE, fileEncoding = "UTF-8-BOM")
pilot_data
```

```{r}
# Selecting relevant columns
pilot_data_df <- pilot_data %>% select(Trial, SubTrial, Subject, Session, Phase.Trial., Procedure.Trial., MisinfoStatement, Statement, BeliefBase.RESP, Belief.RESP, Familiarity.RESP, TestItem.RESP, OtherAnswer.RESP, CR.RESP, Alternate, Target, StatementType, Topic, L2.Recall.Class, L1.Recall.Class)
pilot_data_df

pilot_data_df %<>% arrange(Trial, SubTrial, Subject, Session, Phase.Trial., Procedure.Trial., MisinfoStatement, Statement, BeliefBase.RESP, Belief.RESP, Familiarity.RESP, TestItem.RESP, OtherAnswer.RESP, CR.RESP, Alternate, Target, StatementType, Topic, L2.Recall.Class, L1.Recall.Class)
pilot_data_df
```


```{r}
# Test Phase
cued_recall <- filter(pilot_data_df, Procedure.Trial. == "Test")
cued_recall
```

```{r}
# Create binary variables for each response type (L2 correct, L1 intrusion, ambiguous, error)
cued_recall$L2_Correct <- ifelse(cued_recall$L2.Recall.Class == "2", 1, 0)
cued_recall$L1_Intrusion <- ifelse(cued_recall$L2.Recall.Class == "1", 1, 0)
cued_recall$Ambiguous <- ifelse(cued_recall$L2.Recall.Class == "A", 1, 0)
cued_recall$Error <- ifelse(cued_recall$L2.Recall.Class == "E", 1, 0)

# Create binary variables for each response type (L1 correct, L2 intrusion, ambiguous, error)
cued_recall$L1_Correct <- ifelse(cued_recall$L1.Recall.Class == "1", 1, 0)
cued_recall$L2_Intrusion <- ifelse(cued_recall$L1.Recall.Class == "2", 1, 0)
cued_recall$Ambiguous <- ifelse(cued_recall$L1.Recall.Class == "A", 1, 0)
cued_recall$Error <- ifelse(cued_recall$L1.Recall.Class == "E", 1, 0)

# Create variable for classifying statements as corrections
cued_recall$Correction_Remember <- ifelse(cued_recall$CR.RESP == 1, "Remembered", "Not Remembered")

# Create variable for classifying statements as corrections and correctly recalling list 1 misinformation (correction recollection)
cued_recall$Correction_Recollect <- ifelse(cued_recall$L1.Recall == 1, "Recollected", "Not Recollected")
```


```{r}
# Convert variables to factors (shortened form)
cued_recall %>% mutate_at(c("Subject", "Session", "Phase.Trial.", "Topic", "StatementType", "Statement", "MisinfoStatement", "Correction_Remember", "Correction_Recollect"), factor)
cued_recall
```

```{r}
# Create variable for control in glmers
moreControl <- glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4))
```


```{r}
# Summarize List 2 recall accuracy
cued_recall_l2_acc <- group_by(cued_recall, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$L2_Correct, conf.int = .95, B = 10000))))
cued_recall_l2_acc

# Summarize List 1 intrusion rates
cued_recall_l1_intru <- group_by(cued_recall, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$L1_Intrusion, conf.int = .95, B = 10000))))
cued_recall_l1_intru

# Summarize correction classification rates
cued_recall_class <- group_by(cued_recall, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$CR.RESP, conf.int = .95, B = 10000))))
cued_recall_class

# Summarize List 1 recall accuracy
cued_recall_l1_acc <- group_by(cued_recall, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$L1_Correct, conf.int = .95, B = 10000))))
cued_recall_l1_acc

# Summarize belief ratings made at test
Belief_ratings <- group_by(cued_recall, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))
Belief_ratings

# Filter for Phase 1
phase1_data <- pilot_data_df %>% filter(Procedure.Trial. == c("List1Proc1", "List1Proc2"))
phase1_data

# Summarize baseline belief ratings made during Phase 1
BeliefBase_ratings <- group_by(phase1_data, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$BeliefBase.RESP, conf.int = .95, B = 10000))))
BeliefBase_ratings

# Summarize Familiarity ratings made during Phase 1
Familiarity_ratings <- group_by(phase1_data, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$Familiarity.RESP, conf.int = .95, B = 10000))))
Familiarity_ratings
```
```{r}
# Create data frame with only correction statement types
cued_recall_correct <- filter(cued_recall, StatementType == "Correction")
cued_recall_correction_label <- filter(cued_recall, StatementType == "Correction_Label")
cued_recall_correction_Misinfo <- filter(cued_recall, StatementType == "Correction_Misinfo")
cued_recall_correction_statementtypes <- rbind(cued_recall_correct, cued_recall_correction_label, cued_recall_correction_Misinfo)

# Compute counts and proportions for each item type
plot_df <- group_by(cued_recall, StatementType) %>%
  summarise(n = length(L2_Correct)) %>%
  mutate(prop = 1)
plot_df$Correction_Recollect <- "All"
plot_df

plot_df_boot <- group_by(cued_recall, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$L2_Correct, conf.int = .95, B = 10000))))

plot_df_boot

plot_df_uncond <- merge(plot_df, plot_df_boot)

plot_df_uncond$StatementType <- c("Correction", "Correction Label", "Misinformation Reminder", "Repeated")

plot_df_uncond

# Compute counts and proportions for corrections conditionalized on recollection in List 2
plot_df_cond <- cued_recall_correction_statementtypes %>%
  group_by(StatementType, Correction_Recollect) %>%
  summarise(n = length(L2_Correct)) %>%
  mutate(prop = n / sum(n))
plot_df_cond

plot_df_cond_boot <- cued_recall_correction_statementtypes %>%
  group_by(StatementType, Correction_Recollect) %>%
  do(data.frame(rbind(smean.cl.boot(.$L2_Correct, conf.int = .95, B = 10000))))
plot_df_cond_boot

plot_df_cond <- merge(plot_df_cond, plot_df_cond_boot)

plot_df_cond$StatementType <- c("Correction (Recollection)", "Correction (Recollection)", "Correction Label (Recollection)", "Correction Label (Recollection)", "Misinformation Reminder (Recollection)", "Misinformation Reminder (Recollection)")

plot_df_cond

# Bind data frames
l2_recall_bubble_df <- rbind(plot_df_uncond, plot_df_cond)

l2_recall_bubble_df
```

```{r fig.height=6, fig.width=14}
# Re-arrange factor levels
l2_recall_bubble_df$StatementType <- factor(l2_recall_bubble_df$StatementType, levels = c("Repeated", "Correction", "Correction (Recollection)", "Correction Label", "Correction Label (Recollection)", "Misinformation Reminder", "Misinformation Reminder (Recollection)"))
# Visualize List 2 recall

# Create data frames for line segments
panel1a <- data.frame(x = 3.1, y = .572, xend = 3.9, yend = c(.60, .49))
panel1b <- data.frame(x = 4.1, y = .601, xend = 4.9, yend = c(.72, .28))

# Plot List 1 correct recall for all responses and A-B, A-D conditionalized on change recollection
p1 <- ggplot(l2_recall_bubble_df, aes(x = StatementType, y = Mean, color = Correction_Recollect)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(), size = .4, width = 0, show.legend = FALSE) +
  geom_point(aes(size = prop)) +
  scale_color_manual("Response Classification", values = c("All" = "black", "Recollected" = "forestgreen", "Not Recollected" = "firebrick3")) +
  guides(size = FALSE, color = FALSE) +
  scale_x_discrete(labels = c("Repeated", "Correction", "Correction \n(Recollection)", "Correction Label", "Correction Label \n(Recollection)", "Misinformation Reminder", "Misinformation Reminder \n(Recollection)")) +
  scale_y_continuous(name = "Correct Recall", limits = c(0, 1), breaks = seq(0, 1, .1)) +
  labs(x = "Statement Type") +
  theme(
    legend.key = element_rect(fill = "transparent", size = 0),
    legend.key.height = unit(1.2, "cm"),
    legend.key.width = unit(.8, "cm"),
    legend.text = element_text(size = 10),
    strip.background = element_blank(),
    strip.text.x = element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y = element_text(size = 16, color = "black", margin = margin(0, 0, 0, 8)),
    axis.text.x = element_text(size = 11, color = "black"),
    axis.text.y = element_text(size = 11, color = "black"),
    axis.title.x = element_text(size = 16, margin = margin(8, 0, 0, 0)),
    axis.title.y = element_text(size = 16, margin = margin(0, 8, 0, 0)),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(size = .75, fill = NA, color = "black")
  )
p1
```

Fit Mixed Effects Model to List 2 Correct Recall and Extract Estimated Probabilities

```{r}
# gmler for list 2 recall data (all responses)
L2recall_glmer <- glmer(L2_Correct ~ StatementType + (1 | Subject) + (1 | Topic), family = binomial, data = cued_recall, control = lmerControl(check.nlev.gtr.1 = "ignore"))

# Run ANOVA for List 2 recall for all item types
Anova(L2recall_glmer)


# Pairwise comparisons for List 2 recall for all items types
# emmeans(L2recall_glmer, list(pairwise ~ StatementType), type = "response")
```


```{r}
# dataframe for conditional analyses of correct recall
cued_recall_changed <- cued_recall %>%
  filter(StatementType == c("Correction", "Correction_Label", "Correction_Misinfo"))

# gmler for list 2 recall data (corrected statements conditionalized on correction detection)
L2recall_cr_glmer <- glmer(L2_Correct ~ StatementType + Correction_Recollect + StatementType * Correction_Recollect + (1 | Subject) + (1 | Topic), family = binomial, data = cued_recall_changed, control = glmerControl(check.nlev.gtr.1 = "ignore"))

# Run ANOVA for List 2 recall for all item types
Anova(L2recall_cr_glmer)


# Pairwise comparisons for List 2 recall for all items types
# emmeans(L2recall_cr_glmer, list(pairwise ~ Correction_Recollect, pairwise ~ StatementType, pairwise ~ StatementType | Correction_Recollect), type = "response")
```

```{r}
# Compute counts and proportions for each item type
plot_df <- group_by(cued_recall, StatementType) %>%
  summarise(n = length(L1_Intrusion)) %>%
  mutate(prop = 1)
plot_df$Correction_Remember <- "All"
plot_df

plot_df_boot <- group_by(cued_recall, StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$L1_Intrusion, conf.int = .95, B = 10000))))

plot_df_boot

plot_df_uncond <- merge(plot_df, plot_df_boot)

plot_df_uncond$StatementType <- c("Correction", "Correction Label", "Misinformation Reminder", "Repeated")

plot_df_uncond

# Compute counts and proportions for corrections conditionalized on detection in List 2
plot_df_cond <- cued_recall_correction_statementtypes %>%
  group_by(StatementType, Correction_Remember) %>%
  summarise(n = length(L1_Intrusion)) %>%
  mutate(prop = n / sum(n))

plot_df_cond_boot <- cued_recall_correction_statementtypes %>%
  group_by(StatementType, Correction_Remember) %>%
  do(data.frame(rbind(smean.cl.boot(.$L1_Intrusion, conf.int = .95, B = 10000))))

plot_df_cond <- merge(plot_df_cond, plot_df_cond_boot)

plot_df_cond$StatementType <- c("Correction (Remembered)", "Correction (Remembered)", "Correction Label (Remembered)", "Correction Label (Remembered)", "Misinformation Reminder (Remembered)")
plot_df_cond

# Bind data frames
l1_intru_bubble_df <- rbind(plot_df_uncond, plot_df_cond)

l1_intru_bubble_df
```
```{r fig.height=6, fig.width=14}
# Re-arrange factor levels
l1_intru_bubble_df$StatementType <- factor(l1_intru_bubble_df$StatementType, levels = c("Repeated", "Correction", "Correction (Remembered)", "Correction Label", "Correction Label (Remembered)", "Misinformation Reminder", "Misinformation Reminder (Remembered)"))

# Visualize List 1 intrusions

# Create data frames for line segments
panel1a <- data.frame(x = 3.1, y = .212, xend = 3.9, yend = c(.10, .34))
panel1b <- data.frame(x = 5.1, y = .103, xend = 5.9, yend = c(.06, .23))

# Plot List 1 correct recall for all responses and A-B, A-D conditionalized on change recollection
p2 <- ggplot(l1_intru_bubble_df, aes(x = StatementType, y = Mean, color = Correction_Remember)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(), size = .4, width = 0, show.legend = FALSE) +
  geom_point(aes(size = prop)) +
  scale_color_manual("Response Classification", values = c("All" = "black", "Remembered" = "forestgreen", "Not Remembered" = "firebrick3")) +
  guides(size = FALSE, color = FALSE) +
  scale_x_discrete(labels = c("Repeated", "Correction", "Correction \n(Remembered)", "Correction Label", "Correction Label \n(Remembered)", "Misinformation Reminder", "Misinformation Reminder \n(Remembered)")) +
  scale_y_continuous(name = "Correct Recall", limits = c(0, 1), breaks = seq(0, 1, .1)) +
  labs(x = "Statement Type") +
  theme(
    legend.key = element_rect(fill = "transparent", size = 0),
    legend.key.height = unit(1.2, "cm"),
    legend.key.width = unit(.8, "cm"),
    legend.text = element_text(size = 10),
    strip.background = element_blank(),
    strip.text.x = element_text(size = 16, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y = element_text(size = 16, color = "black", margin = margin(0, 0, 0, 8)),
    axis.text.x = element_text(size = 11, color = "black"),
    axis.text.y = element_text(size = 11, color = "black"),
    axis.title.x = element_text(size = 16, margin = margin(8, 0, 0, 0)),
    axis.title.y = element_text(size = 16, margin = margin(0, 8, 0, 0)),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(size = .75, fill = NA, color = "black")
  )
p2
```

Fit Mixed Effects Model to List 1 Intrusions and Extract Estimated Probabilities

```{r}
# gmler for list 1 intrusion data (all responses)
L1_intr_glmer <- glmer(L1_Intrusion ~ StatementType + (1 | Subject) + (1 | Topic), family = binomial, data = cued_recall, control = lmerControl(check.nlev.gtr.1 = "ignore"))

# Run ANOVA for List 1 intrusions for all item types
Anova(L1_intr_glmer)

# Pairwise comparisons for List 1 intrusions for all items types
# emmeans(L1_intr_glmer, list(pairwise ~ StatementType), type = "response")
```
```{r}
# gmler for list 1 intrusion data (corrected statements conditionalized on correction remembering)
# L1intrusion_cr_glmer <- glmer(L1_Intrusion ~ StatementType + Correction_Remember + StatementType * Correction_Remember + (1 | Subject) + (1 | Topic), family = binomial, data = cued_recall_changed, control = glmerControl(check.nlev.gtr.1 = "ignore"))

# Run ANOVA for list 1 intrusion for all item types
# Anova(L1intrusion_cr_glmer)

# Pairwise comparisons for list 1 intrusion for all items types
# emmeans(L1intrusion_cr_glmer, list(pairwise ~ Correction_Remember, pairwise ~ StatementType, pairwise ~ StatementType | Correction_Remember, pairwise ~ Correction_Remember | StatementType), type = "response")
```
```{r fig.height=12, fig.width=14}
# Combine List 2 recall and List 1 intrusion plots
recall_intrus_comb <- grid.arrange(p1, p2, ncol = 1)

recall_intrus_comb
```

```{r}
# Create data frame for stacked bar graph for correction classification and correct misinformation recall
ChangeClassProp_All <- cued_recall_class
ChangeClass_L1_Recall_All <- cued_recall_l1_acc
ChangeClassProp_All
ChangeClass_L1_Recall_All

StatementType <- ChangeClassProp_All$StatementType
Mean <- (ChangeClassProp_All$Mean - ChangeClass_L1_Recall_All$Mean)
Lower <- ChangeClassProp_All$Lower
Upper <- ChangeClassProp_All$Upper
List_1_Recall <- c("Not Recalled", "Not Recalled", "Not Recalled", "Not Recalled")


# Data frame with difference in change.resp & list 1 correct recall probabilities with CIs for Change.Det.Prop_All
change_class_no_l1 <- data.frame(StatementType, Mean, Lower, Upper, List_1_Recall)
change_class_no_l1

List_1_Recall <- c("Recalled", "Recalled", "Recalled", "Recalled")
l1_recall_all <- data.frame(ChangeClass_L1_Recall_All, List_1_Recall)
l1_recall_all

change_class_misinfo_df <- rbind(change_class_no_l1, l1_recall_all)
change_class_misinfo_df

# Change names of item type levels
change_class_misinfo_df$StatementType <- c("Correction", "Correction Label", "Misinformation Reminder", "Repeated", "Correction", "Correction Label", "Misinformation Reminder", "Repeated")
change_class_misinfo_df
```

```{r fig.height=4, fig.width=8}
# Re-arrange factor levels
change_class_misinfo_df$StatementType <- factor(change_class_misinfo_df$StatementType, levels = c("Repeated", "Correction", "Correction Label", "Misinformation Reminder"))

# Plot change classification and List 1 recall rates
sp <- ggplot(change_class_misinfo_df, aes(x = StatementType, y = Mean, fill = List_1_Recall)) +
  geom_bar(stat = "identity", position = "dodge", width = .65) +
  geom_bar(color = "black", stat = "identity", size = .65, width = .65) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), width = 0, size = .65) +
  scale_x_discrete(labels = c("Repeated", "Correction", "Correction Label", "Misinformation Reminder")) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1.2), breaks = seq(0, 1, .1)) +
  scale_fill_manual(values = c("Recalled" = "dark gray", "Not Recalled" = "white")) +
  xlab("Statement Type") +
  ylab("Correction Classification") +
  guides(fill = guide_legend(title = "Misinformation Recall")) +
  theme(
    legend.position = c(.15, .78),
    legend.key = element_rect(color = "black", size = 0),
    legend.title = element_text(size = 12),
    legend.key.height = unit(.75, "cm"),
    legend.key.width = unit(.75, "cm"),
    legend.text = element_text(size = 10),
    strip.background = element_blank(),
    strip.text.x = element_text(size = 14, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y = element_text(size = 14, color = "black", margin = margin(0, 0, 0, 8)),
    axis.ticks.x = element_line(size = 0, color = "white"),
    axis.ticks.y = element_line(size = .65, color = "black"),
    axis.text.x = element_text(size = 12, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    axis.title.x = element_text(size = 14, margin = margin(8, 0, 0, 0)),
    axis.title.y = element_text(size = 14, margin = margin(0, 8, 0, 0)),
    title = element_text(vjust = 2, size = 14),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(size = 1.25, fill = NA, color = "black")
  )

sp
```

Fit Mixed Effects Model to Change Classifications and Extract Estimated Probabilities

```{r}
# gmler for change classification data (all responses)
change_class_glmer <- glmer(CR.RESP ~ StatementType + (1 | Subject) + (1 | Topic), family = binomial, data = cued_recall, control = lmerControl(check.nlev.gtr.1 = "ignore"))

# Run ANOVA for change classification for all item types
Anova(change_class_glmer)

# Pairwise comparisons for change classification for all items types
# emmeans(change_class_glmer, list(pairwise ~ StatementType), type = "response")
```

Fit Mixed Effects Model to Change Recollection and Extract Estimated Probabilities

```{r}
# gmler for list 1 recall data (all responses)
change_recollection_glmer <- glmer(L1_Correct ~ StatementType + (1 | Subject) + (1 | Topic), family = binomial, data = cued_recall, control = lmerControl(check.nlev.gtr.1 = "ignore"))

# Run ANOVA for list 1 recalll for all item types
Anova(change_recollection_glmer)

# Pairwise comparisons for list 1 recall for all items types
# emmeans(change_recollection_glmer, list(pairwise ~ StatementType), type = "response")
```

```{r}
# Summarize belief ratings
belief_ratings_summary <- cued_recall %>%
  group_by(StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))
belief_ratings_summary

# Summarize belief ratings for L2 Correct
belief_ratings_summary <- cued_recall %>%
  group_by(StatementType, Correction_Recollect) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))
belief_ratings_summary
```
```{r}
# Summarize belief ratings made at test for List 2 correct recall accuracy
belief_ratings_L2 <- filter(cued_recall, L2_Correct == 1) %>%
  group_by(StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))
belief_ratings_L2$Response <- "L2_Correct"

belief_ratings_L2

belief_ratings_cond_L2 <- filter(cued_recall, StatementType == c("Correction", "Correction_Label", "Correction_Misinfo"), L2_Correct == 1) %>%
  group_by(StatementType, Correction_Recollect) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))
belief_ratings_L2$Response <- "L2_Correct_Cond"

belief_ratings_cond_L2

# Summarize belief ratings made at test conditionalized on List 1 intrusions
belief_ratings_L1 <- filter(cued_recall, L1_Intrusion == 1) %>%
  group_by(StatementType) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))
belief_ratings_L1$Response <- "L1_Intrusion"

belief_ratings_L1

belief_ratings_cond_L1 <- filter(cued_recall, StatementType == c("Correction", "Correction_Label", "Correction_Misinfo"), L1_Intrusion == 1) %>%
  group_by(StatementType, Correction_Remember) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))
belief_ratings_L1$Response <- "L1_Intrusion_Cond"

belief_ratings_cond_L1

# Combine dataframes

belief_L2_L1 <- rbind(belief_ratings_L2, belief_ratings_L1)
belief_L2_L1$Mean <- as.numeric(belief_L2_L1$Mean)
belief_L2_L1$Response <- as.factor(belief_L2_L1$Response)
belief_L2_L1
```
```{r}
# Create bubble plots for belief ratings for correct List 2 recall

# Compute counts and proportions for each item type
plot_df <- group_by(cued_recall, StatementType) %>%
  filter(L2_Correct == 1) %>%
  summarise(n = length(L2_Correct)) %>%
  mutate(prop = 1)
plot_df$Correction_Recollect <- "All"
plot_df

plot_df_boot <- group_by(cued_recall, StatementType) %>%
  filter(L2_Correct == 1) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))

plot_df_boot

plot_df_uncond <- merge(plot_df, plot_df_boot)

plot_df_uncond$StatementType <- c("Correction", "Correction Label", "Misinformation Reminder", "Repeated")

plot_df_uncond

# Compute counts and proportions for corrections conditionalized on detection in List 2
plot_df_cond <- cued_recall_correction_statementtypes %>%
  filter(L2_Correct == 1) %>%
  group_by(StatementType, Correction_Recollect) %>%
  summarise(n = length(L2_Correct)) %>%
  mutate(prop = n / sum(n))

plot_df_cond_boot <- cued_recall_correction_statementtypes %>%
  filter(L2_Correct == 1) %>%
  group_by(StatementType, Correction_Recollect) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))

plot_df_cond <- merge(plot_df_cond, plot_df_cond_boot)

plot_df_cond$StatementType <- c("Correction (Recollection)", "Correction (Recollection)", "Correction Label (Recollection)", "Correction Label (Recollection)", "Misinformation Reminder (Recollection)", "Misinformation Reminder (Recollection)")

plot_df_cond

# Bind data frames
l2_recall_belief_bubble_df <- rbind(plot_df_uncond, plot_df_cond)

l2_recall_belief_bubble_df
```


```{r fig.height=6, fig.width=14}
# Re-arrange factor levels
l2_recall_belief_bubble_df$StatementType <- factor(l2_recall_belief_bubble_df$StatementType, levels = c("Repeated", "Correction", "Correction (Recollection)", "Correction Label", "Correction Label (Recollection)", "Misinformation Reminder", "Misinformation Reminder (Recollection)"))
l2_recall_belief_bubble_df

# Visualize List 2 recall
# Create data frames for line segments
panel1a <- data.frame(x = 3.1, y = .572, xend = 3.9, yend = c(.60, .49))
panel1b <- data.frame(x = 4.1, y = .601, xend = 4.9, yend = c(.72, .28))

# Plot List 1 correct recall for all responses and A-B, A-D conditionalized on change recollection
b1 <- ggplot(l2_recall_belief_bubble_df, aes(x = StatementType, y = Mean, color = Correction_Recollect)) +
  geom_errorbar(aes(ymin = Lower, ymax = Upper), position = position_dodge(), size = .4, width = 0, show.legend = FALSE) +
  geom_point(aes(size = prop)) +
  geom_segment(data = panel1a, aes(x = x, y = y, xend = xend, yend = yend), color = "black", arrow = arrow(length = unit(0.3, "cm"))) +
  geom_segment(data = panel1b, aes(x = x, y = y, xend = xend, yend = yend), color = "black", arrow = arrow(length = unit(0.3, "cm"))) +
  scale_color_manual("Response Classification", values = c("All" = "black", "Recollected" = "forestgreen", "Not Recollected" = "firebrick3")) +
  # facet_grid()+
  guides(size = FALSE, color = FALSE) +
  scale_x_discrete(labels = c("Repeated", "Correction", "Correction \n(Recollection)", "Correction Label", "Correction Label \n(Recollection)", "Misinformation Reminder", "Misinformation Reminder \n(Recollection)")) +
  scale_y_continuous(name = "Belief Rating", limits = c(1, 6.2), breaks = seq(1, 6, 1)) +
  labs(x = "Statement Type") +
  theme(
    legend.key = element_rect(fill = "transparent", size = 0),
    legend.key.height = unit(1.2, "cm"),
    legend.key.width = unit(.8, "cm"),
    legend.text = element_text(size = 10),
    strip.background = element_blank(),
    strip.text.x = element_text(size = 18, color = "black", margin = margin(0, 0, 8, 0)),
    strip.text.y = element_text(size = 18, color = "black", margin = margin(0, 0, 0, 8)),
    axis.text.x = element_text(size = 11, color = "black"),
    axis.text.y = element_text(size = 12, color = "black"),
    axis.title.x = element_text(size = 16, margin = margin(8, 0, 0, 0)),
    axis.title.y = element_text(size = 16, margin = margin(0, 8, 0, 0)),
    panel.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(size = 1.25, fill = NA, color = "black")
  )
b1
```



```{r}
# gmler for belief ratings for L2 correct recall (all item types)
# belief_l2_correct_lmer <- lmer(Belief.RESP ~ StatementType + (1 | Subject) + (1 | Topic), data = cued_recall, subset = L2_Correct == "1", control = lmerControl(check.nlev.gtr.1 = "ignore"))

# Run ANOVA
# Anova(belief_l2_correct_lmer)

# Pairwise comparisons
# emm_options(pbkrtest.limit = 3406)
# emm_options(lmerTest.limit = 3406)
# emmeans(belief_l2_correct_lmer, list(pairwise ~ StatementType), type = "response")
```

```{r}
# L2_Correct only data frame
cued_recall_L2_Correct <- filter(cued_recall, L2_Correct == "1")

# gmler for belief ratings for L2 correct recall (corrections and retractions conditionalized)
# belief_l2_correct_cond_lmer <- lmer(Belief.RESP ~ StatementType + Correction_Recollect + StatementType * Correction_Recollect + (1 | Subject) + (1 | Topic), data = subset(cued_recall_L2_Correct, StatementType == c("Correction", "Correction_Label", "Correction_Misinfo")))

# Run ANOVA
# Anova(belief_l2_correct_cond_lmer)

# Pairwise comparisons
# emmeans(belief_l2_correct_cond_lmer, list(pairwise ~ StatementType, pairwise ~ Correction_Recollect, pairwise ~ Correction_Recollect | StatementType), type = "response")
```

```{r}
# Create bubble plots for belief ratings for list 1 intrusions

# Compute counts and proportions for each item type
plot_df <- group_by(cued_recall, StatementType) %>%
  filter(L1_Intrusion == 1) %>%
  summarise(n = length(L1_Intrusion)) %>%
  mutate(prop = 1)
plot_df$Correction_Remember <- "All"
plot_df

plot_df_boot <- group_by(cued_recall, StatementType) %>%
  filter(L1_Intrusion == 1) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))

plot_df_boot

plot_df_uncond <- merge(plot_df, plot_df_boot)

plot_df_uncond$StatementType <- c("Correction", "Correction Label", "Misinformation Reminder", "Repeated")

plot_df_uncond

# Compute counts and proportions for corrections conditionalized on detection in List 2
plot_df_cond <- cued_recall_correction_statementtypes %>%
  filter(L1_Intrusion == 1) %>%
  group_by(StatementType, Correction_Remember) %>%
  summarise(n = length(L1_Intrusion)) %>%
  mutate(prop = n / sum(n))

plot_df_cond_boot <- cued_recall_correction_statementtypes %>%
  filter(L1_Intrusion == 1) %>%
  group_by(ItemType, Correction_Remember) %>%
  do(data.frame(rbind(smean.cl.boot(.$Belief.RESP, conf.int = .95, B = 10000))))

plot_df_cond <- merge(plot_df_cond, plot_df_cond_boot)

plot_df_cond$ItemType <- c("Correction (Remembered)", "Correction (Remembered)", "Correction Label (Remembered)", "Correction Label (Remembered)", "Misinformation Reminder (Remembered)")

plot_df_cond

# Bind data frames
l1_intru_belief_bubble_df <- rbind(plot_df_uncond, plot_df_cond)
l1_intru_belief_bubble_df

```


```{r}
# gmler for belief ratings for L1 intrusions (all item types)
belief_l1_intrusion_lmer <- lmer(Belief.RESP ~ StatementType + (1 | Subject) + (1 | Topic), data = cued_recall, subset = L1_Intrusion == "1")

# Run ANOVA
Anova(belief_l1_intrusion_lmer)

# Pairwise comparisons
# emm_options(pbkrtest.limit = 3403)
# emm_options(lmerTest.limit = 3403)
emmeans(belief_l1_intrusion_lmer, list(pairwise ~ StatementType), type = "response")
```

```{r}
# L1_Intrusion only data frame
cued_recall_L1_Intrusion <- filter(cued_recall, L1_Intrusion == "1")

# gmler for belief ratings for L1 intrusions (corrections and retractions conditionalized)
# belief_l1_intrusion_cond_lmer <- lmer(Belief.RESP ~ StatementType + Correction_Remember + StatementType * Correction_Remember + (1 | Subject) + (1 | Topic), data = subset(cued_recall_L1_Intrusion, StatementType == c("Correction", "Correction_Label", "Correction_Misinfo")))

# Run ANOVA
Anova(belief_l1_intrusion_cond_lmer)

# Pairwise comparisons
# emm_options(pbkrtest.limit = 4257)
# emm_options(lmerTest.limit = 4257)
# emmeans(belief_l1_intrusion_cond_lmer, list(pairwise ~ StatementType, pairwise ~ Correction_Remember, pairwise ~ Correction_Remember | StatementType, pairwise ~ StatementType | Correction_Remember), type = "response")
```
